---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

  library(magrittr)

```

# `envModel`: Model floristic clusters as a function of environmental variables

<!-- badges: start -->
<!-- badges: end -->

The goal of `envModel` is to help prepare data and run models (currently only random forest) to predict group membership as a function of environmental variables. Reduce correlated and 'unimportant' environmental variables, run quick random forest runs over many clusterings outputting only confusion matrix, then choose an area of clustering space for a 'good' model and run random forest, iteratively adding trees until results stabilise between iterations.

## Installation

`envModel` is not on [CRAN](https://CRAN.R-project.org).

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dew-landscapes/envModel")
```

## Contents of `envModel`

The following functions and data sets are provided in `envModel`. 

```{r, echo = FALSE, warning = FALSE}

  get_name_title <- function(text) {
    
    tibble::enframe(text
                    , name = NULL
                    , value = "description"
                    ) %>%
      dplyr::filter(grepl("title", description)) %>%
      dplyr::mutate(description = gsub("\\\\|title", "", description)
                    , description = gsub("^\\{|\\}$", "", description)
                    )
    
  }

  manuals <- fs::dir_info("man") %>%
    dplyr::select(path) %>%
    dplyr::filter(grepl("Rd$", path)
                  , !grepl("pipe", path)
                  ) %>%
    dplyr::mutate(object = gsub("man\\/|\\.Rd","",path)
                  , class = purrr::map_chr(object, ~envFunc::vec_to_sentence(class(get(.))))
                  , text = purrr::map(path, readLines)
                  , text = purrr::map(text, get_name_title)
                  , object = paste0("envModel::"
                                    , object
                                    , ""
                                    )
                  , object = dplyr::if_else(class == "function"
                                            , paste0(object
                                                     , "()"
                                                     )
                                            , object
                                            )
                  , object = paste0("`", object, "`")
                  ) %>%
    tidyr::unnest(cols = c(text))

  knitr::kable(manuals[,2:4])

```
